Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-18 2_SSL_EES/article/article_main.tex
updated acknowledgements section

\section*{Acknowledgements}
This research is supported by a grant of the Alfred P. Sloan Foundation titled \href{http://web.archive.org/web/20200623065733/https://sloan.org/grant-detail/8567}{\textit{“What factors drive innovation in energy technologies? The role of technology spillovers and government investment”}}. Michael Weinold further gratefully acknowledges support by the \href{https://www.studienstiftung.ch/}{Swiss Study Foundation}. We would like to thank Venkatesh Narayanamurti, Gabriel Chan, Anna Goldstein, Didier Sornette, and participants of the SPIE West 2021 Conference and \href{https://www.ceenrg.landecon.cam.ac.uk/}{C-EENRG} Seminar Series of the University of Cambridge for many helpful discussions and feedback. We also express our deep gratitude to all interviewees for their willingness to participate in this study and their valuable contributions. Support by German consumer organization \textit{Stiftung Warentest} in providing access to their archive is gratefully acknowledged.

>>>>

\section*{Acknowledgements}
This research is supported by the grant from the Alfred P. Sloan Foundation titled \textit{“What factors drive innovation in energy technologies? The role of technology spillovers and government investment”}. Michael Weinold further gratefully acknowledges financial support from the Swiss Study Foundation. We would like to thank Venkatesh Narayanamurti, Gabriel Chan, Anna Goldstein, Didier Sornette, and participants of the SPIE West 2021 Conference and C-EENRG Seminar Series of the University of Cambridge for many helpful discussions and feedback. We also express our deep gratitude to all interviewees for their willingness to participate in this study and their invaluable contributions.
